The proposed pipeline indicates intriguing nuances of the packing problem. The use of a minimal, suction-based end-effector is a cost-effective, simple and relatively robust way to pick objects but does not easily allow for complex grasp reasoning, regrasping, or within-hand manipulation. The proposed pipeline achieves high accuracy by leveraging the compliance of the suction cup and the environment, while the object is attached. It uses robust reasoning to incrementally correct errors, instead of compounding them. While it can be argued that better baseline components can be developed to minimize uncertainty, the overall philosophy of robust, minimal, and compliant reasoning remains unchanged. 

The proposed system and primitives can also deal with cubic objects with different sizes and can be extended to non-cubic objects by adapting the object models. The key adaptation corresponds to identifying an appropriate packing arrangement $\atarget$ (potentially labeled in this case) in the target bin and the corresponding picking order from the initial bin. Future work will also explore speeding up performance and dealing with algorithmic challenges: the combinatorial reasoning over possible placements, physics-based reasoning to further improve pushing and toppling, as well as extending to more adaptive end-effectors. The platform can also be utilized as a training testbed for reinforcement learning to automatically discover robust primitives for solving packing tasks.

%https://preview.overleaf.com/public/vygnpnpqtbct/images/6836fea5b56bab9aa94fc612378769a9aaa648b9.jpeg